---
title: "ESM204_HW3"
author: "Shellby Johnson"
date: "May 16, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, include = FALSE}

library(tidyverse)
library(stargazer)

whaledata <- read_csv("HW3Data.csv")

```

##1
```{r, echo=FALSE, results='asis'}

whalevote_lm <- lm(vote ~ age + income + NEP + risk + bid, data = whaledata)

summary(whalevote_lm)

#put results in stargazer table

lm_table_whalevote <- stargazer(whalevote_lm, type = "html", align = TRUE, title = "**Table 1. Multivariate Linear Regression of Voting for Whale Protection**", covariate.labels = c("Age 40-50", "Age 30-40", "Age 50-60", "Age 18-30", "Income Top 1 Percent", "Income Poor", "Income Rich", "Income Very Rich", "NEP", "Risk Reduction", "Cost to Respondent"), dep.var.labels=c("Voting Response For Whale Protection"), single.row = TRUE)


```

##2
Based on this regression, what can you say about the value of a single prevented whale death? (Hint: Think about how risk reduction for all whales translates into the number of whale deaths avoided)

V(yes) = 1.20 + (.020*Ageto30) + (-.020*Ageto40) + (.010 *Ageto50) + (-.016*Ageto60) + (.003 * IncomePoor) + (.007*Rich) + (.047*IncomeVeryRich) + (.009 * IncomeOnePercent) + (0.016*** (0.002) * NEP) + (0.001 (0.001) * RiskReduction) +(-0.001*BID)

(-0.001*BID) = .119670 - (.714*Voteyes) + (.020*Ageto30) + (-.020*Ageto40) + (.010 *Ageto50) + (-.016*Ageto60) + (.003 * IncomePoor) + (.007*Rich) + (.047*IncomeVeryRich) + (.009 * IncomeOnePercent) + (0.016*** (0.002) * NEP) + (0.001 (0.001) * RiskReduction)

4% reduction/whale = $2.79
Response Variable:
Vote = 0.714

##3
Pick three arbitrary respondents. For each of those respondents, estimate their WTP for a VSR program offering 60% risk reduction. 

```{r}

#Estimated WTP for respondent 150; NEP = 8; Income = poor; Age = tothirty; vote = yes

respondent_150 <- (0.119670 - 0.714 + (0.0204401*1) + (0.0027386*1) + (0.0158639 *8) + 
                     (0.0007445 * 60))/ -0.0010699

#Estimated WTP for respondent 300; NEP = 44; Income = 1 %; Age = tosixty; vote = yes

respondent_300 <- (0.119670 - 0.714 + (-0.0162261 *1) + (0.0088282*1) + (0.0158639 *44) + 
                     (0.0007445 * 60))/ -0.0010699

#Estimated WTP for respondent 448; NEP = 13; Income = 1 %; Age = tofifty; vote = yes

respondent_448 <- (0.119670 - 0.714 + (0.0099816*1) + (0.0088282*1) + (0.0158639 *13) + 
                     (0.0007445 * 60))/ -0.0010699

```


##4
Now repeat this process and estimate the mean WTP for a VSR program offering 60% risk
reduction among Santa Barbara County households.

##5
If there are 150,000 households in Santa Barbara County, estimate the total benefit of a VSR program to these households.

##6
Based only on these benefits, do the benefits of the VSR program outweigh the costs?

